% Providing localization that are not automatically covered by polyglossia.
% The commands are provided by KOMAscript.
% Maintaining the list is not the easiest, but currently likely the best approach.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Colophon
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\providecaptionname{english}{\TransCompiledOn}{Compiled on}
\providecaptionname{german}{\TransCompiledOn}{Kompiliert am}

\providecaptionname{english}{\TransLatexClass}{Class}
\providecaptionname{german}{\TransLatexClass}{Klasse}

\providecaptionname{english}{\TransGenerator}{Generator}
\providecaptionname{german}{\TransGenerator}{Generiert durch}

\providecaptionname{english}{\TransCensorNotice}{CENSORED VERSION}
\providecaptionname{german}{\TransCensorNotice}{ZENSIERTE VERSION}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Task
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\providecaptionname{english}{\TransPlaceDate}{Place \& Date}
\providecaptionname{german}{\TransPlaceDate}{Ort \& Datum}

\providecaptionname{english}{\TransTopic}{Topic}
\providecaptionname{german}{\TransTopic}{Thema}

\providecaptionname{english}{\TransTask}{Task}
\providecaptionname{german}{\TransTask}{Problemstellung}

\providecaptionname{english}{\TransFor}{For}
\providecaptionname{german}{\TransFor}{Für}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Declaration of Authorship
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\providecaptionname{english}{\TransAuthorshipDeclTitle}{Declaration of Authorship}
\providecaptionname{german}{\TransAuthorshipDeclTitle}{Erklärung zur Eigenständigkeit}

%
% No warranty these wordings are valid in your case!
%
\providecaptionname{english}{\TransAuthorshipDeclText}{%
    I, \@author{}, hereby declare to be the sole, independent author of the
    \@documenttype{} submitted here.
    No other than the cited references have been used.
    Any content directly or indirectly obtained from external sources has been marked up as such.
    This thesis has neither been submitted to a second examination authority nor been published.%
}%

\providecaptionname{german}{\TransAuthorshipDeclText}{%
    Hiermit bestätige ich, \@author{}, der alleinige und selbstständige Autor der hier
    vorgelegten \@documenttype{} zu sein.
    Keine anderen als die angegebenen Quellen wurden benutzt.
    Jeglicher aus externen Quellen direkt oder indirekt bezogene Inhalt ist als solcher markiert.
    Diese Arbeit wurde weder einer anderen Prüfungsbehörde vorgelegt noch veröffentlicht.
}%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Cleveref
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\providecaptionname{english}{\TransReaction}{Reaction}
\providecaptionname{german}{\TransReaction}{Reaktion}
\providecaptionname{english}{\TransReactions}{Reactions}
\providecaptionname{german}{\TransReactions}{Reaktionen}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Glossary
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\providecaptionname{english}{\TransGreek}{Greek}
\providecaptionname{german}{\TransGreek}{Griech.}

\providecaptionname{english}{\TransRoman}{Roman}
\providecaptionname{german}{\TransRoman}{Röm.}

\providecaptionname{english}{\TransOther}{Other}
\providecaptionname{german}{\TransOther}{Andere}

\providecaptionname{english}{\TransTerms}{Terms}
\providecaptionname{german}{\TransTerms}{Begriffe}

\providecaptionname{english}{\TransNames}{Names}
\providecaptionname{german}{\TransNames}{Namen}

\providecaptionname{english}{\TransSubscripts}{Subscripts}
\providecaptionname{german}{\TransSubscripts}{Indizes}

\providecaptionname{english}{\TransSuperscripts}{Superscripts}
\providecaptionname{german}{\TransSuperscripts}{Hochgest.}

\providecaptionname{english}{\TransSubSuperTitle}{Sub- and Superscripts}
\providecaptionname{german}{\TransSubSuperTitle}{Indizes}

\providecaptionname{english}{\TransUnit}{Unit}
\providecaptionname{german}{\TransUnit}{Einheit}

\providecaptionname{english}{\TransPhysicalQuantity}{Phys.\ Qtt.}
\providecaptionname{german}{\TransPhysicalUnit}{Phys.\ Größe}

\providecaptionname{english}{\TransFirstUse}{\nth{1} Use}
\providecaptionname{german}{\TransFirstUse}{Einführ.}

\providecaptionname{english}{\TransShort}{Short}
\providecaptionname{german}{\TransShort}{Kurz}

\providecaptionname{english}{\TransContinued}{continued}
\providecaptionname{german}{\TransContinued}{fortgesetzt}

\providecaptionname{english}{\TransGlossaryLegend}{
    Marked (\specificsymbolmark) symbols possess a mass\-/specific variant in which
    the symbol is written in lowercase and the unit is extended by
    \si[per-mode=reciprocal]{\per\kilogram}.
    Alternative symbols are specified following the \alternativesymbolmark{} mark.
    International symbols are specified in brackets.%
}
\providecaptionname{german}{\TransGlossaryLegend}{
    Markierte (\specificsymbolmark) Symbole besitzen eine massenspezifische Variante,
    bei der das Symbol als Kleinbuchstabe gesetzt und die Einheit entsprechend um
    \si[per-mode=reciprocal]{\per\kilogram} erweitert wird.
    Alternative Symbole sind nach \alternativesymbolmark{} angegeben,
    internationale Symbole in eckigen Klammern.%
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% SCRLayer
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\providecaptionname{english}{\TransBlankPage}{Rest of this page intentionally left blank.}
\providecaptionname{german}{\TransBlankPage}{Rest der Seite absichtlich freigelassen.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Lists of ...
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\providecaptionname{english}{\TransIllustrativeElements}{Illustrative Elements}
\providecaptionname{german}{\TransIllustrativeElements}{Veranschaulichende Elemente}

\providecaptionname{english}{\TransListOfIllustrations}{List of Illustrations}
\providecaptionname{german}{\TransListOfIllustrations}{Illustrationsverzeichnis}

\providecaptionname{english}{\TransListing}{Code Listing}
\providecaptionname{english}{\TransListings}{Code Listings}% Plural for cleveref

\providecaptionname{german}{\TransListing}{Code}
\providecaptionname{german}{\TransListings}{Codes}% Plural for cleveref

\providecaptionname{english}{\TransListOfListings}{List of Code}
\providecaptionname{german}{\TransListOfListings}{Codeverzeichnis}

\providecaptionname{english}{\TransListOfExamples}{List of Examples}
\providecaptionname{german}{\TransListOfExamples}{Beispielverzeichnis}

\providecaptionname{english}{\TransExample}{Example}
\providecaptionname{german}{\TransExample}{Beispiel}
\providecaptionname{english}{\TransExamples}{Examples}
\providecaptionname{german}{\TransExamples}{Beispiele}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Bibliography
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\providecaptionname{english}{\TransFurtherReadingTitle}{Further Reading}
\providecaptionname{german}{\TransFurtherReadingTitle}{Weitere Literatur}

\providecaptionname{english}{\TransFurtherReadingText}{%
    The following references were used in this work but not cited in the text body;
    they are provided here as\-/is.
}
\providecaptionname{german}{\TransFurtherReadingText}{%
    Die folgenden Quellen wurden im Rahmen dieser Arbeit benutzt, jedoch nicht
    explizit zitiert.
    Sie sind hier der Vollständigkeit halber aufgeführt.
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Other
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\providecaptionname{english}{\TransConstant}{const}
\providecaptionname{german}{\TransConstant}{konst}

\providecaptionname{english}{\TransAdaptedFrom}{Adapted from}
\providecaptionname{german}{\TransAdaptedFrom}{Adaptiert von}
